Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance

### 2017-07-28 ms_pre_post.Rmd
First part of Discussion initial revision

Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations. Rather, such evolution is likely to involve multiple interacting phenotypes resulting in the potential for feedback and degeneracy (i.e., functional redundancy) among phenotypes under selection. For example, strong inbreeding depression in offspring fitness is widely hypothesised to drive selection for inbreeding avoidance, which could consequently drive selection for polyandry [e.g., @Zeh1997; @Jennions2000; @Tregenza2002]. Inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs. We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given the pre-existence of the other. We present our model and simulation results as a tool for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system. While the logic of our model can be usefully applied to constructing hypotheses within and across empirical systems, accurate quantitative prediction would require additional detail and the incorporation of empirical data for model parameterisation.

>>>>

Evolution of different reproductive strategies cannot be presumed to occur in isolation from each other in real-world populations. Rather, there is likely to be considerable potential for feedbacks and degeneracy (i.e., functional redundancy) among multiple interacting phenotypes. For example, inbreeding avoidance could be manifested through both pre-copulatory and post-copulatory mechanisms and associated polyandry, meaning that simultaneous evolution of each phenotype might be defined by degeneracy in addition to trait-specific costs.

We used individual-based modelling to highlight fundamental but theoretically under-developed relationships between evolution of polyandry and pre-copulatory versus post-copulatory inbreeding strategy given (1) hard constraints on evolution of post-copulatory inbreeding strategy, (2) asymmetric costs of pre-copulatory and post-copulatory inbreeding strategy, and (3) evolution of one inbreeding strategy phenotype given pre-existence of the other. We present our model and simulation results as tools for thinking more clearly about the dynamics of simultaneously evolving reproductive strategies, not for making accurate quantitative predictions for any specific system. While the logic of our model can be usefully applied to construct hypotheses within and across empirical systems, accurate quantitative prediction would require additional empirical detail and data for model parameterisation.
